The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-10-15 borel-regularity.tex
Do small clarifications

%% \textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}. Suppose $\Omega_\beta$ contains the ray $\mathcal{J}_{\zeta, \beta}^\theta$. In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ of holomorphic functions on $\Omega_\beta$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta - \beta|^\sigma$ as $\zeta$ approaches $\beta$. When $\sigma>-1$, the singularity at $\zeta = \beta$ is integrable. Hence, the Laplace transform $\laplace_{\zeta, \beta}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > \Lambda$ in the cotangent space $T_{\zeta = \beta}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
%%

@@

@@

Let $\phi,\psi$ be two holomorphic functions on $B$. Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$. The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
\color{Turquoise}
Choose $\phi \in \singexpalg{\sigma}(\Omega_\alpha),\psi \in \singexpalg{\sigma'}(\Omega_\beta)$ \begin{todo}[refine]\end{todo}. Choose a translation coordinate $\zeta$ on $B$. The convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral

@@

%%line segment in $B^2$ where $\zeta_\alpha(a)$ goes from $0$ to $\zeta_{\alpha + \beta}$ and $\zeta_\beta(a')$ goes from $\zeta_{\alpha + \beta}$ to $0$ with $\zeta(a) + \zeta(a') = \zeta$ at all times.

%%where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a) = \zeta_{\alpha + \beta}$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a') = \zeta_{\alpha + \beta}$ to $\zeta_\beta(a') = 0$.
\end{definition}
\color{black}
\begin{revised}
\begin{lemma}
Take $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$, with $\sigma,\sigma'\in (-1,\infty)$. The convolution $\phi\ast_{\zeta,\alpha,\beta}\psi$ belongs to $\singexp{\sigma''}{\Lambda''}(\Omega_{\alpha+\beta})$, where $\Lambda'' = \Lambda + \Lambda'$ and $\sigma'' = 1+\sigma+\sigma'$.  \end{lemma}    
\begin{proof}
\begin{align*}
\left|\phi\ast_{\zeta,\alpha,\beta}\psi\right|&\le\int_{\mathcal{S}_{\zeta,\alpha,\beta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
& = \int_0^1|\phi(a)|\,|\psi(a')|\,|\zeta_{\alpha+\beta}| dt\,,
\end{align*}
where we use $d\zeta(a)=d\zeta_\alpha(a)=d(t\zeta_{\alpha+\beta})=\zeta_{\alpha+\beta}\,dt$. 
Since $\phi$ and $\psi$ have bounded norms,
\begin{align*}
|\zeta_{\alpha+\beta}|\int_0^1 |\phi(a)|\,|\psi(a')|\, dt&\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|^{1+\sigma+\sigma'}\int_0^1  |t|^{\sigma}e^{\Lambda t |\zeta_{\alpha+\beta}|}\,|1-t|^{\sigma'}e^{\Lambda' (1-t)|\zeta_{\alpha+\beta}|}\,dt\\
&\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\int_0^1  t^{\sigma}\,(1-t)^{\sigma'}\,dt\\
&\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\,.
\end{align*}
\end{proof}
\end{revised}
\begin{old}
The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined.\end{old}

On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$. The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
\begin{prop}\label{prop:convolution_iso_laplace}
\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} \begin{revised}For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have\end{revised} \begin{old}Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined. Then\end{old}
\begin{equation}\label{eqn:laplace-convol1}
\laplace_{\zeta,0}[\phi\ast_{\zeta,0}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
\end{equation}
\begin{todo}
Add assumption that the Laplace transform of the convolution is well defined. I think we could simply assume $\phi,\psi$ being of exponential type.    
\end{todo}
\end{prop}
\begin{proof}
\begin{revised}
The left-hand side of equation~\eqref{eqn:laplace-convol1} expands to
\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_{\mathcal{J}_{\zeta, 0}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,. \]
In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $0$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta$ to $0$.

The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$. Thus, on $\mathcal{N}$, we have the identity
\begin{align*}
d\zeta(a) + d\zeta(a') & = d\zeta \\
d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta\\
d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
\end{align*}
which we can substitute into the integral above to get
\begin{align*}
\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\end{align*}

By construction, the range of $\zeta$ on $\mathcal{N}$ is $[0, \infty)$. From the definitions of the paths $\mathcal{S}(\zeta)$ and $\mathcal{S}'(\zeta)$, it follows that the ranges of $\zeta(a)$ and $\zeta(a')$ on $\mathcal{N}$ are also both $[0, \infty)$. In fact, projection onto the $a$ and $a'$ factors of $B^3$ identifies $\mathcal{N}$ with $\mathcal{J}_{\zeta(a), 0} \times \mathcal{J}_{\zeta(a'), 0} \subset B^2$. We can therefore factorize the integral above using Fubini's theorem, yielding the desired identity:
\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \left[ \int_{\mathcal{J}_{\zeta(a), 0}} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \left[ \int_{\mathcal{J}_{\zeta(a'), 0}} e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\
&=\zeta_\alpha\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
where $\zeta_\alpha(a)=s\zeta_\alpha$ and consequently $\zeta_\alpha(a')=(1-s) \zeta_\alpha$.  
First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$. \begin{todo}[Right now, we're only assuming that $\phi$ and $\psi$ have well-defined Laplace transforms, which doesn't imply that they're uniformly of exponential type]\end{todo} It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
\big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi(a)|\,|\psi(a')|\\
&\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
& \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}\,.
Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$. This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.
Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi(a) \psi(a')\,ds \\
&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi(a) \psi(a')\,ds 
by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}
&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi(a) \psi(a') \\
&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a')\,\frac{\zeta_\alpha(a')}{(1-s)^2}\,e^{-z\zeta_\alpha(a')} e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\,\psi(a') 
Using that $\zeta_\alpha(a)=\zeta_\alpha(a')\frac{s}{1-s}$ holds on the integration contour, we find
&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a')\,\int_0^1 ds\,\frac{\zeta_\alpha(a')}{(1-s)^2}e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\\
&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta_\alpha,0}} d\zeta_\alpha(a)\, e^{-z\zeta_\alpha(a)} \phi(a)\\
where as $s$ varies in $[0,1]$ we get that $a$ follows the ray $\mathcal{J}_{\zeta_\alpha,0}$ \begin{todo}[check this statement]\end{todo}.
More generally we can show that the product of two Laplace transforms based at different points is the Laplace transform of the convolution.

@@

Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transforms $\laplace_{\zeta,\alpha}\phi$ and $\laplace_{\zeta,\beta}\psi$ are well defined. Then 

@@

\laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha+\beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.

@@

\begin{todo}
[\textbf{V} add $\theta$, or explain that it's missing, Fix proof] [\textbf{A} read through proof]
The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}}  \phi(a)\,\psi(a')\, d\zeta_\alpha(a)\,. \]
In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta_\alpha)$ where $\zeta_\alpha(a)$ runs from $\beta$ to $\zeta_\alpha$, while $a'$ follows the straight path $\mathcal{S}'(\zeta_\alpha)$ where $\zeta_\alpha(a')$ runs from $\zeta_\alpha - \beta$ to $0$.
\begin{draft}
The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,. \]
In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta - (\alpha + \beta)$ to $0$.

The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$. Thus, on $\mathcal{N}$, we have the identity
\begin{align*}
d\zeta(a) + d\zeta(a') & = d\zeta \\
d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
\end{align*}
which we can substitute into the integral above to get
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\end{align*}
\begin{todo}Now we need to explain why the grid lines can be projected to $\mathcal{J}_{\zeta(a), \alpha}$ and $\mathcal{J}_{\zeta(a'), \beta}$. Something seems off here. The tip of the wedge $\mathcal{N}$ should be at $\zeta = \alpha + \beta$, since that's the beginning of the ray $\mathcal{J}_{\zeta, \alpha + \beta}$. At that point, though, according to our definitions, $\mathcal{S}(\zeta)$ should consist of the point $\zeta(a) = \alpha + \beta$, and $\mathcal{S}'(\zeta)$ should consist of the point $\zeta(a') = 0$.

In my drawings, I assumed that the tip of the wedge $\mathcal{N}$ would be at the point where $\zeta(a) = \alpha$, $\zeta(a') = \beta$, and $\zeta = \alpha + \beta$. Now I'm skeptical about that. Is that point even in $\mathcal{N}$? If so, what distinguishes it from all the other points on the line $\zeta(a) + \zeta(a') = \alpha + \beta$? Since $\alpha$ and $\beta$ can vary without changing the left-hand side of equation~\eqref{eqn:gen-laplace-convol}, we must need to make a choice somewhere\ldots

Maybe we need to change the statement to
\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,. \]
I think the argument might wrap up neatly in that case.
\end{todo}
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_{?} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \int_{?} e^{z\zeta(a')}\,\psi(a')\,d\zeta(a')
\end{align*}
\end{draft}

\color{violet}
In the convolution integral, $a$ and $a'$ move so that $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$ while $\zeta(a')$ goes from $\zeta_{\alpha+\beta}$ to $0$.

\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=\int_{\mathcal{J}_{\zeta,\alpha+\beta}}d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\, \psi(a')\, d\zeta(a)
\end{align*}

Equivalently, $a$ and $a'$ move so that $\zeta_{\textcolor{magenta}{\alpha}}(a)$ runs from $\zeta_{\alpha+\beta}$ to $0$ while $\zeta_{\textcolor{magenta}{\beta}}(a')$ goes from $\zeta$ to $0$. In particular, we introduce the parameter $s\in [0,1]$ so that $\zeta(a)=(1-s)(\alpha+\beta)+s\zeta-\beta$ and $\zeta(a')=(1-s)\zeta+\beta$. 
\color{black}
\begin{revised}
The convolution product can be rewritten by introducing the coordinates $\zeta_\beta$ and $\zeta_{-\beta}$:
\begin{align*}
\phi \ast_{\zeta, \alpha+\beta} \psi &= \int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
&=\int_{\substack{\mathcal{S}(\zeta_{\beta}) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_{\beta}(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\,,
\end{align*}
where $\mathcal{S}(\zeta_{\beta})$ is the line segment from $\zeta_\beta(a)=\alpha$ to $\zeta_\beta(a)=\zeta_\beta$ and similarly, $\mathcal{S}'(\zeta_{-\beta})$ is the line segment from $\zeta_{-\beta}(a')=\zeta_\alpha$ to $\zeta_{-\beta}(a')=\beta$. This change of coordinates simplifies our computations by showing how the convolution product depends on the base points of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.

Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution  
    \phi \ast_{\zeta, \alpha+\beta} \psi
    &=\int_{\substack{\mathcal{S}(\zeta_\beta) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_\beta(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
    &=\zeta_{\alpha+\beta}\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
\begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\zeta_\beta(a)=(1-s)\alpha+s\zeta_\beta$ and consequently $\zeta_{-\beta}(a')=\beta s+(1-s)\zeta_\alpha$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
    \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=e^{-z(\alpha+\beta)}\laplace_{\zeta_{\alpha+\beta},0}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]\\
    &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi(a)\,\psi(a')\,ds \\

>>>>

@@

% \begin{definition}\label{def:convolution}
% Let $\phi,\psi$ be two holomorphic functions on $B$. Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$. The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
% \begin{equation}%%\label{eq:convolution_def}
% \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
% \end{equation}
% where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
% \end{definition}

@@

Choose a translation coordinate $\zeta$ on $B$. Let $\Omega_\alpha \subset B$ be an open set with the point $\zeta = \alpha$ on its boundary, and let $\Omega_\beta \subset B$ be an open set with $\zeta = \beta$ on its boundary. For any $\phi \in \singexpalg{\sigma}(\Omega_\alpha)$ and $\psi \in \singexpalg{\sigma'}(\Omega_\beta)$, the convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral

@@

\begin{notation*}
 When $\alpha=\beta$ we denote $\ast_{\zeta,\alpha,\beta}$ simply by $\ast_{\zeta,\alpha}$. For $\alpha=\beta=0$, Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}, so we will denote $\ast_{\zeta,0}$ simply by $\ast_\zeta$. \begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}   
\end{notation*}
Take $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$, with $\sigma,\sigma'\in (-1,\infty)$. The convolution $\phi\ast_{\zeta,\alpha,\beta}\psi$ belongs to $\singexp{\sigma''}{\Lambda''}(\Omega_{\alpha+\beta})$, where $\Lambda'' = \Lambda + \Lambda'$ and $\sigma'' = 1+\sigma+\sigma'$.
\left|\phi\ast_{\zeta,\alpha,\beta}\psi\right|&\le\int_{\mathcal{S}_{\zeta,\alpha,\beta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
& = \int_0^1|\phi(a)|\,|\psi(a')|\,|\zeta_{\alpha+\beta}|\,dt\,,
where we use $d\zeta(a)=d\zeta_\alpha(a)=d(t\zeta_{\alpha+\beta})=\zeta_{\alpha+\beta}\,dt$. 
Since $\phi$ and $\psi$ have bounded norms,
|\zeta_{\alpha+\beta}|\int_0^1 |\phi(a)|\,|\psi(a')|\,dt &\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|\int_0^1  |\zeta_\alpha(a)|^{\sigma}e^{\Lambda  |\zeta_{\alpha}(a)|}\,|\zeta_\beta(a')|^{\sigma'}e^{\Lambda' |\zeta_{\beta}(a')|}\,dt\\
&= \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|^{1+\sigma+\sigma'}\int_0^1  |t|^{\sigma}e^{\Lambda t |\zeta_{\alpha+\beta}|}\,|1-t|^{\sigma'}e^{\Lambda' (1-t)|\zeta_{\alpha+\beta}|}\,dt\\
&\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\int_0^1  t^{\sigma}\,(1-t)^{\sigma'}\,dt\\
&\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\,.
The product of two Laplace transforms based at different points is the Laplace transform of the convolution.

@@

For any $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$ with $\sigma,\sigma'\in (-1,\infty)$, we have

@@

\laplace^\theta_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha,\beta} \psi] = \laplace^\theta_{\zeta,\alpha}[\phi]\,\laplace^\theta_{\zeta,\beta}[\psi]\,.

@@

More generally, this proposition holds for any holomorphic functions $\phi$ and $\psi$ for which the convolution and all of the Laplace transforms in equation~\eqref{eqn:gen-laplace-convol} are well-defined.
For simplicity, we will write out the proof for $\theta = 0$. The proof for general $\theta$ is analogous.

The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
\begin{align*}
\laplace_{\zeta,\alpha,\beta}[\phi \ast_{\zeta,\alpha, \beta} \psi] &= \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\mathcal{S}_{\zeta,\alpha,\beta}} \phi(a)\,\psi(a')\, d\zeta(a)\,.
\end{align*}
where $\mathcal{S}_{\zeta, \alpha, \beta}$ is the path described in Definition~\ref{def:convolution}. On this path, the equation
\begin{equation}\label{eq:slice-plane}
\zeta_\alpha(a) + \zeta_\beta(a') = \zeta_{\alpha+\beta}
\end{equation}
holds, and the coordinates $\zeta_\alpha(a)$ and $\zeta_\beta(a')$ have the same argument as $\zeta_{\alpha+\beta}$. In particular, over the ray $\mathcal{J}_{\zeta, \alpha+\beta}$, the coordinates $\zeta_\alpha(a)$, $\zeta_\beta(a')$ and $\zeta_{\alpha+\beta}$ are all real and non-negative.\footnote{For general $\theta$, we have the condition that $\zeta_\alpha(a)$, $\zeta_\beta(a')$ and $\zeta_{\alpha+\beta}$ all lie on the ray $e^{i\theta}[0, \infty)$.} The point where $\mathcal{S}_{\zeta, \alpha, \beta}$ starts has $\zeta_\alpha(a) = 0$, and the point where $\mathcal{S}_{\zeta, \alpha, \beta}$ ends has $\zeta_\beta(a') = 0$.

The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}_{\zeta, \alpha, \beta}$ within the complex three-dimensional space $B^3$:
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
The coordinates $\zeta_\alpha(a)$, $\zeta_\beta(a')$, $\zeta_{\alpha+\beta}$ parameterize $B^3$, and the real wedge $\mathcal{N}_{\zeta, \alpha, \beta}$ is cut out by equation~\eqref{eq:slice-plane} and the conditions
a & \in \mathcal{J}_{\zeta, \alpha} \\
a' & \in \mathcal{J}_{\zeta, \beta} \\
\zeta_{\alpha+\beta} & \in [0, \infty)\,.
Equation~\eqref{eq:slice-plane} can be rewritten as $\zeta(a) + \zeta(a') = \zeta$, which implies the identities
d\zeta(a) + d\zeta(a') & = d\zeta \\
d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,.
We can substitute the last identity into the integral over $\mathcal{N}_{\zeta, \alpha, \beta}$ to get
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] & = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
& = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right].
Thinking of $\mathcal{N}_{\zeta, \alpha, \beta}$ as the graph of $\zeta_\alpha(a) + \zeta_\beta(a')$ over the quadrant $\mathcal{J}_{\zeta, \alpha} \times \mathcal{J}_{\zeta, \beta}$, we can use Fubini's theorem to express the integral as the product
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \left[ \int_{\mathcal{J}_{\zeta, \alpha}} e^{-z\zeta}\,\phi\,d\zeta \right] \left[ \int_{\mathcal{J}_{\zeta,\beta}} e^{-z\zeta}\,\psi\,d\zeta \right]. \]
\begin{corollary}\label{prop:convolution_iso_laplace}
For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have
\begin{equation}\label{eqn:laplace-convol1}
\laplace_{\zeta,0}[\phi\ast_{\zeta}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
\end{corollary}
On a domain $\Omega$ which is star-shaped around $\zeta = 0$, the convolution product $\ast_{\zeta}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega)$. The Laplace transform $\laplace_{\zeta, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta}$.
